\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-01-29 correct.tex
Updated

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1} gives a
  value \texttt{d}, provided $D$ is a non empty set, such that for any
  given reaction time $\hj{\Delta}$ \hj{in the range of} $BCRT \leq
  \Delta \leq WCRT$, $M \leq \Delta \times d \leq N$ holds.
\label{th:1}
\end{theorem}
\begin{proof}
  We use case analysis and contradiction to prove the above theorem.
  \begin{compactenum}[\hspace{0.25cm} 1.]
  \item Proof for case $\Delta = WCRT$: Assume \mbox{$d \times WCRT <
      M$}, then $d < \frac{M}{WCRT}$. $BCRT \leq WCRT$, by definition,
    hence, $\frac{M}{WCRT} \leq \frac{M}{BCRT}$. Thus for the assumption
    to hold, $d < \frac{M}{BCRT}$, which contradicts
    Lemma~\ref{lemma:1}. The assumption $d \times WCRT >N$ is trivially
    proven from Lemma~\ref{lemma:1}.
  \item Proof for case $\Delta = BCRT$: Like above, the assumption $d
    \times BCRT < M$ is trivially proven from Lemma~\ref{lemma:1}. For
    $d \times BCRT > N$ to hold, $d > \frac{N}{BCRT}$ should hold. But,
    $BCRT \leq WCRT$, by definition, hence, $\frac{N}{BCRT} \geq
    \frac{N}{WCRT}$, which again contradicts Lemma~\ref{lemma:1}.
  \item Proof for case $BCRT < \Delta < WCRT$: For $d \times \Delta < M$
    to hold, $d < \frac{M}{\Delta}$ should hold. By definition, $\Delta
    > BCRT$, thus, $\frac{M}{BCRT} < \frac{M}{\Delta}$, hence, $d <
    {M}{BCRT}$ should hold, which contradicts Lemma~\ref{lemma:1}. We
    can prove the other case $d \times \Delta \leq N$, using the upper
    bound from Lemma~\ref{lemma:1} similarly.
  \end{compactenum}
\end{proof}

@@

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1}
  \textbf{does not} give a value \texttt{d}, such that for \textbf{all}
  given reaction times $T$ in the range of $BCRT > T > WCRT$, $M \leq T
  \times d \leq N$ holds.
\end{theorem}

@@

The proofs for correctness, completeness, and soundness for
Algorithm~\ref{alg:2} are similar to those of Algorithm~\ref{alg:1}.

>>>>

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1} gives a
  value \texttt{d}, provided $D$ is a non empty set, such that for any
  given reaction time $\hj{\Delta}$ \hj{in the range of} $BCRT \leq
  \Delta \leq WCRT$, $M \leq \Delta \times d \leq N$ holds.
\label{th:1}
\end{theorem}
\begin{proof}
  We use case analysis and contradiction to prove the above theorem.
  \begin{compactenum}[\hspace{0.25cm} 1.]
  \item Proof for case $\Delta = WCRT$: Assume \mbox{$d \times WCRT <
      M$}, then $d < \frac{M}{WCRT}$. $BCRT \leq WCRT$, by definition,
    hence, $\frac{M}{WCRT} \leq \frac{M}{BCRT}$. Thus for the assumption
    to hold, $d < \frac{M}{BCRT}$, which contradicts
    Lemma~\ref{lemma:1}. The assumption $d \times WCRT >N$ is trivially
    proven from Lemma~\ref{lemma:1}.
  \item Proof for case $\Delta = BCRT$: Like above, the assumption $d
    \times BCRT < M$ is trivially proven from Lemma~\ref{lemma:1}. For
    $d \times BCRT > N$ to hold, $d > \frac{N}{BCRT}$ should hold. But,
    $BCRT \leq WCRT$, by definition, hence, $\frac{N}{BCRT} \geq
    \frac{N}{WCRT}$, which again contradicts Lemma~\ref{lemma:1}.
  \item Proof for case $BCRT < \Delta < WCRT$: For $d \times \Delta < M$
    to hold, $d < \frac{M}{\Delta}$ should hold. By definition, $\Delta
    > BCRT$, thus, $\frac{M}{BCRT} < \frac{M}{\Delta}$, hence, $d <
    \frac{M}{BCRT}$ should hold, which contradicts Lemma~\ref{lemma:1}. We
    can prove the other case $d \times \Delta \leq N$, using the upper
    bound from Lemma~\ref{lemma:1} similarly.
  \end{compactenum}
\end{proof}

@@

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1}
  \textbf{does not} give a value \texttt{d}, such that for \textbf{all}
  given reaction times $\Delta$ in the range of $BCRT > \Delta > WCRT$,
  $M \leq \Delta \times d \leq N$ holds.
\end{theorem}

@@

The proofs for correctness, completeness, and soundness for
Algorithm~\ref{alg:2} are similar to those of
Algorithm~\ref{alg:1}. Furthermore, the proofs for \texttt{wait\_atleast
  (M)} and \texttt{wait\_exact (M)} can be proven using the same
techniques as shown in Theorem~\ref{th:1}.

### 2014-01-29 delays.tex
Updated things
Updated

The resultant value for \texttt{d} gives the number of logical ticks,
which can run at any physical clock-speed, bounded by the BCRT and the
WCRT of the program and still result in the desired real-time wait
period. Figure~\ref{fig:hrtcssoln} gives the solution space for the
aforementioned calculation. The patterned space is the only overlapping
region and hence gives the solution space for the above example.

@@

The interaction of the low-level execution platform and the described
high-level technique of introducing real-time waits in the SystemJ
language is shown in Figure~\ref{fig:4}. We use static analysis
techniques to find out the WCRT/BCRT of the programs automatically after
rewrites and standard compiler optimizations. We require timing
analyzable platforms, in our case \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}. Moreover, since algorithms~\ref{alg:1}
and~\ref{alg:2} are performed after scheduling for different constraints
such as faster execution time, or reduced power consumption, we
inherently satisfy the criteria of exploiting non-maximal
parallelism. The low-level analysis guarantees a precise WCRT/BCRT for
the logical tick, which is then used for calculating $d$ in
Figure~\ref{fig:3}.

Our compiler has a switch that enables over-approximation as described
in Section~\ref{sec:extend-tehcn-vari} provided the wait requirements
are not met. If this compiler switch is not enabled, the compiler simply
decides to execute the CD periodically, where the period is the
WCRT. WCRT effects the over-approximation or the period of the CD,
irrespective of the solution that the system designer chooses. A large
WCRT results in reduced performance and hence it is essential that the
WCRT be optimized. One can optimize the WCRT of any CD by breaking the
critical paths using the \texttt{pause} construct as we show later in
Section~\ref{sec:experimental-results}.

>>>>

The resultant value for \texttt{d} gives the number of logical ticks,
which can run at any physical clock-speed, bounded by the BCRT and the
WCRT of the program and still result in the desired real-time wait
period. Figure~\ref{fig:hrtcssoln} gives the solution space for the
aforementioned calculation. The patterned space is the only overlapping
region and hence gives the solution space for the above example. It is
possible that $D$ is an empty set, thereby, no solution can be found. We
provide solutions for such cases in the next section.

@@

The interaction of the low-level execution platform and the described
high-level technique of introducing real-time waits in the SystemJ
language is shown in Figure~\ref{fig:4}. We use static analysis
techniques to find out the WCRT/BCRT of the programs automatically after
rewrites and standard compiler optimizations. We require timing
analyzable platforms, in our case \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}. It is worth pointing out that since all
rewrites, including the rewrite for the wait constructs happen before
WCRT/BCRT analysis, this analysis incorporates the affects of the
introduction of the wait statements. Moreover, since
algorithms~\ref{alg:1} and~\ref{alg:2} are performed after scheduling
for different constraints such as faster execution time, or reduced
power consumption, we inherently satisfy the criteria of exploiting
non-maximal parallelism. The low-level analysis guarantees a precise
WCRT/BCRT for the logical tick, which is then used for calculating $d$
in Figure~\ref{fig:3}.

Our compiler has a switch that enables over-approximation as described
in Section~\ref{sec:extend-tehcn-vari} provided the wait requirements
are not met. If this compiler switch is not enabled, the compiler simply
decides to execute the CD periodically, where the period is the
WCRT. WCRT effects the over-approximation and the period of the CD,
irrespective of the solution that the system designer chooses. A large
WCRT results in reduced performance and hence it is essential that the
WCRT be optimized. One can optimize the WCRT of any CD by breaking the
critical paths using the \texttt{pause} construct as we show later in
Section~\ref{sec:experimental-results}.

### 2014-01-29 motivation.tex
Updated

The SystemJ pseudo-code~\cite{amal10} for such a system, along with the
expected timing behavior of the \texttt{wait\_inbetween} statement, is
shown in Figure~\ref{fig:1}. We use the SystemJ language in this paper, 
because being a \textit{Globally Asynchronous Locally
  Synchronous} (GALS) language it helps us easily describe a larger
class of systems (like HRTCS in Figure~\ref{fig:1}) compared to purely
synchronous languages like Esterel. Moreover, being a super-set of
Esterel, SystemJ allows us to explore the marriage of real-time and
logical time, which is equally applicable to the synchronous sub-set.

>>>>

The SystemJ pseudo-code~\cite{amal10} for such a system, along with the
expected timing behavior of the \texttt{wait\_inbetween} statement, is
shown in Figure~\ref{fig:1}. We use the SystemJ language in this paper,
because being a \textit{Globally Asynchronous Locally Synchronous}
(GALS) language it helps us easily describe a larger class of systems
(like HRTCS in Figure~\ref{fig:1}) compared to purely synchronous
languages like Esterel. Moreover, being a super-set of Esterel, SystemJ
allows us to explore the marriage of real-time and logical time not only
in the GALS, but also in the synchronous setting.
